---
title: "R-package: SSDFGP"
subtitle: "Sample Size Determination for Genomic Prediction"
author: "Last edited by: Jen-Hsiang Ou"
date: "Last edited time: `r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
    default_style: "dark"
    downcute_theme: "default"
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
library(badger)
```

<!-- Badges -->

`r badge_lifecycle("experimental")` `r badge_devel("oumarkme/SSDFGP", "blue")` `r badge_doi("not avalible", "yellow")`

------------------------------------------------------------------------

## Introduction

## Installation

```{r eval=FALSE, include=TRUE}
### RUN THIS IN R CONSOLE ###
devtools::install_github("oumarkme/SSDFGP")
library(SSDFGP)
```

You may pull requests or questions at [GitHub issue page](https://github.com/oumarkme/SSDFGP/issues) or directly contact one of us.

## Main function in this package

## Methods

### The growth curve model

The logistic growth curve model was adopted to fit the relationship between the r-score and the training set size.

$$
y = \frac{\alpha}{1 + \exp(\beta - \gamma x)}
$$

-   $y$: the r-score

-   $x$: training set size

-   $\alpha$: unknown parameter relating to the asymptotic

-   $\beta$: intercept on y-axis

-   $\gamma$: rate at which r-score ([Ou et al., 2019](https://doi.org/10.1007/s00122-019-03387-0)) changes from its initial value

### Procedure

1.  Obtain r-scores for given training set sizes ($n_t$: varying from $n_{min}$ to $n_{max}$ by $\delta$).
2.  Obtain the parameter estimates in the logistic growth curve model.

## Authorship

-   Po-Ya Wu \<[Po-Ya.Wu\@hhu.de](mailto:Po-Ya.Wu@hhu.de)\>
    -   Thesis author

    -   Institute for Quantitative Genetics and Genomics of Plants, Heinrich Heine University, Düsseldorf, Germany
-   Jen-Hsiang Ou \<[jen-hsiang.ou\@imbim.uu.se](mailto:jen-hsiang.ou@imbim.uu.se)\>
    -   Package maintainer

    -   Department of Medical Biochemistry and Microbiology, Uppsala University, Uppsala, Sweden
-   Chen-Tuo Liao \<[ctliao\@ntu.edu.tw](mailto:ctliao@ntu.edu.tw)\>
    -   Project administration, supervisor

    -   Department of Agronomy, National Taiwan University, Taipei, Taiwan

## Citation

## Funding and acknowledgment

This research was supported by the Ministry of Science and Technology, Taiwan (grant number: MOST 110-2118-M-002-002-MY2)
